---
title: "Leveraged Return Calculator"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu,
    source_code: https://git.io/vPOCT
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyr)
library(purrr)
library(dplyr)
library(shiny)
library(d3treeR)
library(treemap)
library(stringr)
library(tibble)
library(taucharts)
library(fundManageR)
```


Input Assumptions {.sidebar}
=======================================================================

### Financial Assumptions

Interactive [shiny](shiny.rstudio.com) [flexdashboard](http://rmarkdown.rstudio.com/flexdashboard/) utilizing [fundManageR](https://github.com/abresler/fundManageR)'s leveraged cash flow metric calculator for back of the envelope leveraged cash flow analysis.

```{r inputs}
textInput("assetName", "Asset Name", "Alex's Deal", width = '150px')
# purchase price
textInput("purchase_price", "Purchase Price", "$10,000,000",width = '150px')
textInput("capitalized_acquisition_costs", "Acquisition Costs", "$300,000",width = '150px')
textInput("capital_investment", "Capital Investment", "$200,000",width = '150px')
textInput("revenue", "Revenue", "$1,500,000",width = '150px')
textInput("expenses", "Expenses", "$325,000", width = '150px')
textInput("loan_to_cost", "Loan to Cost", "70%", width = '150px')
numericInput(
  inputId = 'amortization_years',
  label = 'Amortization Period, Years',
  value = 30,
  min = 0,
  step = 1,
  max = 1000,
  width = '120px'
  )
numericInput(
  inputId = 'term_years',
  label = 'Loan Term, Years',
  value = 10,
  min = 1,
  step = 1,
  max = 1000,
  width = '120px'
  )
textInput("interest_rate", "Interest Rate", "3.85%", width = '150px')
selectInput(
  'is_actual_360',
  label = "Actual/360 Interest?",
  choices = c(TRUE, FALSE),
  multiple = F,
  selected = T,
  selectize = T,
  width = '120px'
  )
selectInput(
  'borrow_capital_investment',
  label = "Borrow Capital Investment?",
  choices = c(TRUE, FALSE),
  multiple = F,
  selectize = T,
  width = '120px'
  )
selectInput(
  'include_capitalized_cost',
  label = "Capitalize Acquisition Costs?",
  choices = c(TRUE, FALSE),
  multiple = F,
  selectize = T,
  width = '120px'
  )
selectInput(
  'is_interest_only',
  label = "Interest Only Loan?",
  choices = c(TRUE, FALSE),
  multiple = F,
  selected = FALSE,
  selectize = T,
  width = '120px'
  )
numericInput(
  inputId = 'interest_only_periods',
  label = 'Interest Only Periods',
  value = 0,
  min = 0,
  step = 1,
  max = 1000000,
  width = '120px'
  )
```

Financial Return Table
=======================================================================

Row {data-width=350}
-----------------------------------------------------------------------

```{r}
get_return_data <- 
  reactive({
  return_data <- 
      calculate_leverage_metrics(
      purchase_price = input$purchase_price,
      capitalized_acquisition_costs = input$capitalized_acquisition_costs,
      capital_investment = input$capital_investment,
      revenue = input$revenue,
      expenses = input$expenses,
      loan_to_cost = input$loan_to_cost,
      interest_rate = input$interest_rate,
      borrow_capital_investment = input$borrow_capital_investment,
      include_capitalized_cost = input$include_capitalized_cost,
      leverage_threshold = 1,
      is_interest_only = input$is_interest_only,
      interest_only_periods = input$interest_only_periods,
      is_actual_360 = input$is_actual_360,
      amortization_years = input$amortization_years,
      amortization_months = 0,
      term_years = input$term_years,
      term_months = 0,
      pct_loan_fee = 0,
      return_wide = T,
      return_message = F
    ) %>% 
    mutate(nameAsset = input$assetName) %>% 
    dplyr::select(-idScenario) %>% 
    dplyr::select(nameAsset, everything())
  return(return_data)
})

```

### Return On Cost {.value-box}

```{r}

renderValueBox({
  return_data <- 
  get_return_data()
  rate <- 
    return_data$pctReturnOnCost
  valueBox(
    value = rate,
    icon = "glyphicon-usd",
    color = 'red',
  )
})
```

### Debt Service Coverage {.value-box}

```{r}

renderValueBox({
  return_data <- 
  get_return_data()
  rate <- 
    return_data$ratioDSCRMean
  valueBox(
    value = rate,
    icon = "ion-arrow-graph-up-right"
  )
})
```

### Leverage {.value-box}

```{r}
renderValueBox({
  return_data <- 
  get_return_data()
  rate <- 
    return_data$pctLeverage
  valueBox(
    value = rate,
    icon = "fa-money",
    color = 'red'
  )
})

```

### Cash on Cash {.value-box}

```{r}
# Emit the download rate
renderValueBox({
  return_data <- 
  get_return_data()
  rate <- 
    return_data$pctCashOnCashMean
  valueBox(
    value = rate,
    icon = "fa-area-chart"
  )
})
```


Row
-----------------------------------------------------------------------

### Calculations {data-width=400}
Financial Summary
```{r}
renderTable({
    return_data <- 
    get_return_data()
    return_data %>% t() %>% data.frame(value = .) %>% tibble::rownames_to_column(var = 'item') 
})
```

Financial Return Visualizations
=======================================================================

Row {data-width=350}
-----------------------------------------------------------------------

### Sources and Uses

```{r}
renderD3tree2({
  return_data <-
    get_return_data() %>% 
    gather(item, value, -(nameAsset))
  source_use_df <-
    return_data %>%
    dplyr::slice(1:6) %>%
    dplyr::filter(!item == 'amountBasis') %>%
    dplyr::select(item, value) %>%
    left_join(data_frame(
      item = c(
        "amountPurchasePrice",
        "amountCapitalInvestment",
        "amountCapitalizedCosts",
        "amountLoanProceeds",
        "amountEquity"
      ),
      typeItem = c("use", "use", "use",
                   "source", "source")
    )) %>%
    dplyr::mutate(item = item %>% str_replace_all('amount', '')) %>% 
    suppressMessages()
  
  treemap_viz <-
    source_use_df %>%
    mutate(valueThousands = value %>% abs() / 1000) %>%
    treemap(
      index = c("typeItem", 'item'),
      # structure of the trees
      vSize = "valueThousands",
      # size of the tree
      vColor = "valueThousands",
      # color of the tree
      palette = "RdYlGn",
      fontsize.labels = 8,
      type = "value"
    ) %>%
    d3tree2(rootname = "Sources & Uses")
  
  treemap_viz
})
```

### Cash Flow Summary

```{r tauchart}
renderTaucharts({
  return_data <-
    get_return_data() %>% 
    gather(item, value, -(nameAsset))
  
    return_data %>%
    dplyr::slice(7:13) %>%
    dplyr::select(item, value) %>%
    dplyr::filter(!item == 'meanPayment') %>% 
    mutate(
      label = c(rep("NOI", 3), rep("Leverage", 3)),
      value = value %>% formattable::currency(),
      item = item %>% stringr::str_replace_all('amount', '')
    ) %>%
    tauchart() %>% tau_bar("value", c("label", "item"), 'label', horizontal = TRUE) %>% 
    tau_legend() %>%
    tau_tooltip()
})
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Cash Flow Metrics

```{r tauchart_metrics}
renderTaucharts({
  return_data <-
    get_return_data() %>%
    gather(item, value, -(nameAsset))
  
  return_data %>%
    dplyr::filter(
      item %in% c(
        "pctReturnOnCost",
        "pctDebtYieldInitial",
        "pctCashOnCashMean",
        "pctReturnOnEquity"
      )
    ) %>%
    dplyr::select(item, value) %>%
    mutate(
      label = c(rep("Unleveraged", 2), rep("Leveraged", 2)),
      value = value %>% formattable::percent(),
      item = item %>% stringr::str_replace_all("pct", '')
    ) %>%
    tauchart() %>%
    tau_bar("item", 'value', 'label', horizontal = F) %>%
    tau_guide_y(tick_format = ",.2%", label = '') %>%
    tau_legend() %>%
    tau_tooltip()
})
```

### Deal Metrics

```{r tauchart_metrics3}
renderTaucharts({
  return_data <-
    get_return_data() %>%
    gather(item, value, -(nameAsset))
  
  return_data %>% 
      dplyr::filter(item %in% c("pctLeverage", "pctMarginEBITDA_NOI", 
                                "ratioDSCRMean", "rule72Multiple2x")
      ) %>% 
      dplyr::select(item, value) %>%
      mutate(
        value = value %>% formattable::percent(),
        item = item %>% stringr::str_replace_all("pct", '')
      ) %>%
      tauchart() %>% 
      tau_bar('item', 'value', 'item', horizontal = F) %>% 
      tau_guide_y(tick_format = ",.2f", label = '') %>% 
      tau_guide_x(label = '',padding = 20)  %>% 
      tau_legend() %>%
      tau_tooltip()
})
```