---
title: "ADV Functions: Analyzing SEC Investment Adviser Data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ADV Functions: Analyzing SEC Investment Adviser Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(

collapse = TRUE,
comment = "#>",
eval = FALSE
)
```

## Introduction
This vignette demonstrates fundManageR's ADV data acquisition functions. The SEC requires registered investment advisers to file Form ADV, which contains detailed information about the adviser's business, ownership, clients, employees, disciplinary events, and private funds.

fundManageR provides comprehensive access to this data through several functions:

- `adv_managers_current_period_summary()` - Summary data for all registered advisers
- `adv_managers_metadata()` - Search for advisers by name or CRD number
- `adv_managers_filings()` - Detailed Form ADV section data
- `adv_managers_brochures()` - Form ADV Part 2 brochure text (OCR'd)

## Setup

```{r setup}
library(fundManageR)
library(dplyr)
library(tidyr)
```

## Explore All Registered Advisers

The `adv_managers_current_period_summary()` function downloads summary data for all registered investment advisers from the SEC's most recent ADV filing period.
```{r summary-data}
# Get summary data for all registered advisers
all_advisers <- adv_managers_current_period_summary()

# View the structure
glimpse(all_advisers)

# How many advisers?
nrow(all_advisers)

# Filter to large advisers (>$1B AUM)
large_advisers <- all_advisers %>%
filter(hasAUMGreater1B == TRUE)

nrow(large_advisers)
```

## Search for a Specific Adviser

Use `adv_managers_metadata()
` to search for advisers by name. This is useful when you don't know the CRD number.

```{r search-adviser}
# Search for Blackstone entities
blackstone_entities <- adv_managers_metadata(entity_names = "Blackstone")

# View results
blackstone_entities %>%
select(idCRD, nameEntityManager, cityOfficePrimary, stateOfficePrimary) %>%
head(10)
```

## Get Detailed Filing Data

Once you have a CRD number, use `adv_managers_filings()` to get detailed Form ADV data. This function parses all sections of the ADV filing.

```{r filings-data}
# Get detailed ADV data for Blackstone Management Partners (CRD 136979)
blackstone_data <- adv_managers_filings(
crd_ids = 136979,
all_sections = TRUE,
assign_to_environment = TRUE
)

# This creates multiple data frames in your environment:
# - sectionRegistration
# - section1IdentifyingInfo
# - section5AdvisoryBusinessInformation
# - section7BPrivateFundReporting
# - sectionScheduleAOwners
# - sectionScheduleBIndirectOwners
# - managerRelatedAdvisers
# - and more...
```

### Private Fund Data

Section 7.B contains detailed information about private funds managed by the adviser.

```{r private-funds}
# View private fund data
section7BPrivateFundReporting %>%
select(nameFund, amountGrossAUM, nameAuditorFund) %>%
head(10)

# Count funds by auditor
section7BPrivateFundReporting %>%
count(nameAuditorFund, sort = TRUE)
```

### Related Advisers

Schedule D Section 7.A lists related advisers and their relationships.

```{r related-advisers}
# View related advisers
managerRelatedAdvisers %>%
select(nameBusinessRelatedEntity, nameLegalRelatedEntity,
        isRelatedPersonControlled, isPooledInvestmentSponsor) %>%
head(10)
```
### Ownership Structure

Schedule A and B contain direct and indirect ownership information.

```{r ownership}
# Direct owners (Schedule A)
sectionScheduleAOwners %>%
select(nameOwner, typeOwner, pctOwnership) %>%
head(10)

# Indirect owners (Schedule B)
sectionScheduleBIndirectOwners %>%
select(nameOwner, nameEntityOwned, typeOwnershipInterest) %>%
head(10)
```

## Get Brochure Text

Form ADV Part 2 (the "brochure") contains narrative information about the adviser's services, fees, and conflicts of interest. The `adv_managers_brochures()` function extracts and OCRs this text.

```{r brochures}
# Get brochure text for Blackstone
blackstone_brochures <- adv_managers_brochures(crd_ids = 136979)

# View structure
glimpse(blackstone_brochures)

# The textBrochure column contains the OCR'd text from each page
blackstone_brochures %>%
select(idCRD, nameEntityManager, countPages, textBrochure) %>%
head(5)
```

## Example: Analyzing a Manager

Here's a complete workflow to analyze an investment adviser:

```{r complete-example}
# 1. Search for the manager
apollo <- adv_managers_metadata(entity_names = "Apollo Global")

# 2. Get the primary CRD (usually the largest AUM)
apollo_crd <- apollo %>%
filter(str_detect(nameEntityManager, "APOLLO GLOBAL MANAGEMENT")) %>%
pull(idCRD) %>%
first()

# 3. Get detailed filing data
apollo_filings <- adv_managers_filings(
crd_ids = apollo_crd,
all_sections = TRUE,
assign_to_environment = TRUE
)

# 4. Analyze the data
# How many private funds?
n_funds <- nrow(section7BPrivateFundReporting)

# Total AUM across private funds
total_aum <- section7BPrivateFundReporting %>%
summarise(total = sum(amountGrossAUM, na.rm = TRUE))

# Who are the auditors?
auditors <- section7BPrivateFundReporting %>%
count(nameAuditorFund, sort = TRUE)

# Related advisers
n_related <- nrow(managerRelatedAdvisers)
```

## Tips and Best Practices

1. **CRD Numbers**: Always use CRD numbers when possible - they're unique identifiers. Names can have variations.

2. **Large Datasets**: `adv_managers_current_period_summary()` downloads data for 20,000+ advisers. Consider filtering early.

3. **Rate Limiting**: The SEC may rate-limit requests. Use `furrr::plan(sequential)` for safer sequential processing.

4. **Environment Assignment**: Use `assign_to_environment = TRUE` to get individual data frames for each ADV section.

5. **Nested Data**: Some sections return nested tibbles. Use `tidyr::unnest()` to flatten them.

## Function Reference

| Function | Description |
|----------|-------------|
| `adv_managers_current_period_summary()` | All advisers summary data |
| `adv_managers_metadata()` | Search by name or CRD |
| `adv_managers_filings()` | Detailed Form ADV sections |
| `adv_managers_brochures()` | OCR'd brochure text |
| `adv_period_urls()` | Historical filing period URLs |

## Data Dictionary

Key column prefixes used throughout:

- `id*` - Identifiers (idCRD, idCIK, idSEC)
- `name*` - Entity/person names
- `amount*` - Dollar amounts (formatted as currency)
- `pct*` - Percentages
- `count*` - Counts
- `is*`, `has*` - Boolean flags
- `date*` - Date values
- `url*` - URLs to SEC filings
